---
title: "R Notebook"
output: html_notebook
---

```{r}
# install.packages('vars')
library(vars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
dat1 <- read.csv(file = "AirQualityUCI.csv", sep = ';', stringsAsFactors = FALSE)
dat1 <- dat1[,1:(ncol(dat1)-2)]
dat1 <- dat1[rowSums(is.na(dat1)) == 0,]
head(dat1)
str(dat1)
```
```{r}
dat1$CO.GT. <- gsub(',', '.', dat1$CO.GT.)
dat1$CO.GT. <- as.numeric(dat1$CO.GT.)

dat1$C6H6.GT. <- gsub(',', '.', dat1$C6H6.GT.)
dat1$C6H6.GT. <- as.numeric(dat1$C6H6.GT.)

dat1$T <- gsub(',', '.', dat1$T)
dat1$T <- as.numeric(dat1$T)

dat1$RH <- gsub(',', '.', dat1$RH)
dat1$RH <- as.numeric(dat1$RH)

dat1$AH <- gsub(',', '.', dat1$AH)
dat1$AH <- as.numeric(dat1$AH)
str(dat1)
```

```{r}
dat1['Date_Time'] <- as.POSIXct(paste(dat1$Date, dat1$Time), format="%d/%m/%Y %H.%M.%S")
dat1 <- dat1[, 3:ncol(dat1)]
rownames(dat1) <- dat1$Date_Time
str(dat1)
```
```{r}
dat1 <- dat1[, 1:(ncol(dat1)-1)]
head(dat1)
```
```{r}
for(j in 1:ncol(dat1))
{
  for (i in 2:nrow(dat1))
  {
    if(dat1[i,j] == -200)
    {
      dat1[i,j] = dat1[i-1,j]
    }
  }
}
```

```{r}
# install.packages('forecast')
library(forecast)
```

```{r}
dat1 <- within(dat1, rm(NMHC.GT.))
dat1 <- as.data.frame(scale(dat1))
str(dat1)
```

```{r}
split <- floor(0.9*(nrow(dat1)))
train <- dat1[1:split,]
val <- dat1[split:nrow(dat1),]
str(train)
```
```{r}
var_res <- VAR(train, p = 20, type = 'const', season = (24*3))
```

```{r}
summary(var_res)
```

```{r}
forecast <- predict(var_res, n.ahead = 937, ci = 0.95)
# str(forecast)
```

```{r}
val['Date_Time'] <- rownames(val)
val$Date_Time <- as.POSIXct(val$Date_Time)
head(val)
```
```{r}
# Sample Result
temp <- forecast$fcst$AH[,1]
temp <- as.data.frame(temp)
temp['Date_Time'] <- as.POSIXct(val$Date_Time)
str(temp)
```

```{r}
library(ggplot2)

ggplot()+geom_line(data = val, aes(x = Date_Time, y = AH),color = "#00AFBB", size = 2)+geom_line(data = temp, aes(x = Date_Time, y = temp),color = "red", size = 2)

# line(forecast$fcst$CO.GT.$)
```

```{r}
RMSE = function(m, o){
  sqrt(mean((m - o)^2))
}
```

```{r}
cat("CO.GT. :",RMSE(forecast$fcst$CO.GT.[1],val$CO.GT.), "\n")
cat("PT08.S1.CO. :",RMSE(forecast$fcst$PT08.S1.CO.[1],val$PT08.S1.CO.), "\n")
cat("C6H6.GT. :",RMSE(forecast$fcst$C6H6.GT.[1],val$C6H6.GT.), "\n")
cat("PT08.S2.NMHC. :",RMSE(forecast$fcst$PT08.S2.NMHC.[1],val$PT08.S2.NMHC.), "\n")
cat("NOx.GT. :",RMSE(forecast$fcst$NOx.GT.[1],val$NOx.GT.), "\n")
cat("PT08.S3.NOx. :",RMSE(forecast$fcst$PT08.S3.NOx.[1],val$PT08.S3.NOx.), "\n")
cat("NO2.GT. :",RMSE(forecast$fcst$NO2.GT.[1],val$NO2.GT.), "\n")
cat("PT08.S4.NO2. :",RMSE(forecast$fcst$PT08.S4.NO2.[1],val$PT08.S4.NO2.), "\n")
cat("PT08.S5.O3. :",RMSE(forecast$fcst$PT08.S5.O3.[1],val$PT08.S5.O3.), "\n")
cat("T :",RMSE(forecast$fcst$T[1],val$T), "\n")
cat("RH :",RMSE(forecast$fcst$RH[1],val$RH), "\n")
cat("AH :",RMSE(forecast$fcst$AH[1],val$AH), "\n")
```

